Time Prints of New Physics at Neutrino Telescopes

### 2024-01-05 paper/sections/model.tex
Updates from Overleaf

The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$. As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}. For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different times for two benchmarks 
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
    Jeff needs to write here.
    }
    \label{fig:fluxes}
\end{figure}

>>>>

The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$. As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}. For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrinos at different time for two benchmarks of the Majoron case, in comparison to the standard neutrino flux in \cref{fig:fluxes}. We can observe that the energy of neutrinos from Majoron decay extends to $\unit[100]{Mev}$ and above, as expected. For heavy Majoron case, the resulting neutrino flux typically is larger at later time, manifesting the time delay from slowly moving Majorons. 
The flux for light Majoron case contain very rich physics.
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
    Jeff needs to write here. {\color{red}also need to write the couplings used}
    }
    \label{fig:fluxes}
\end{figure}\\
